\textbf{Evaluating RISC-V Enclaves:}\\ Security Without the Slowdown?

### 2025-09-05 draft_presentation.tex
added new diagrams

@@

@@

%Results
\section{Key Performance Trends and Hardware Bottlenecks}
\label{sec:synthesis}

@@

% Native: orange, rounded top, transparency
\addplot[
    fill={rgb,255:red,230; green,159; blue,0},
    fill opacity=0.8,
    draw=black!60,
    rounded corners=2pt
] coordinates {(CoreMark,100) (Dhrystone,100) (Kyber,100)};

@@

\begin{frame}{Deployment Takeaways}
\begin{block}{Best Practices}
\begin{itemize}
    \item Use NAPOT-aligned, contiguous memory regions.
    \item Consolidate workloads into fewer enclaves.
    \item Batch calls to reduce context switches.
    \item Adapt enclave usage based on task complexity.
\end{itemize}
\end{block}

\begin{alertblock}{Key Principle}
    Balance performance, isolation, and PMP resource usage for optimal efficiency.
\end{alertblock}
\end{frame}

@@

% Future Work and Improvements
\begin{frame}{Hardware Outlook \& Future Directions}
    \only<1>{
\begin{block}{Limitations}
\begin{itemize}
    \item Few PMP entries.
    \item Rigid NAPOT region encoding.
\end{itemize}
\end{block}
    }
    \only<2>{
\begin{alertblock}{Future Opportunities}
\begin{itemize}
    \item More flexible PMP schemes.
    \item Crypto accelerators for enclave workloads.
    \item Software-defined memory isolation models.
\end{itemize}
\end{alertblock}
    }
\end{frame}

>>>>

\section{Background and System Design}

@@

\section{Experimental Setup}

@@

%Results
\section{Results and Hardware Bottlenecks}
\label{sec:synthesis}

@@

% Native: orange, rounded top, tranRecommendationssparency
\addplot[
    fill={rgb,255:red,230; green,159; blue,0},
    fill opacity=0.8,
    draw=black!60,
    rounded corners=2pt
] coordinates {(CoreMark,100) (Dhrystone,100) (Kyber,100)};

@@

\section{Practical Deployment Strategies and Recommendations}

\begin{frame}{Deployment Takeaways}
\begin{block}{Best Practices}
\begin{itemize}
    \only<1>{\item \faMemory\ \textbf{Align memory precisely:} Use NAPOT-aligned, contiguous regions to simplify PMP configuration.}
    \only<2>{\item \faProjectDiagram\ \textbf{Minimize enclave count:} Consolidate workloads to reduce PMP entry usage and management overhead.
    \begin{tikzpicture}[font=\scriptsize,>=stealth]

% --- BEFORE: Multiple enclaves ---
\node[anchor=west] at (-0.5,2.5) {\textbf{Before: Multiple Enclaves}};
\foreach \i in {0,2.5,5} {
  % Enclave box
  \draw[fill=red!20,thick] (\i,1) rectangle +(2,1);
  \node at (\i+1,2.15) {Enclave};
  % Task inside
  \draw[fill=blue!10,thick] (\i+0.5,1.2) rectangle +(1,0.6);
  \node at (\i+1,1.5) {Task};
}

% Arrow between before and after (shorter gap)
\draw[->,thick] (3.5,0.8) -- (3.5,0.2) node[midway,right]{\textbf{Merge}};

% --- AFTER: Single consolidated enclave (moved up) ---
\node[anchor=west] at (-0.5,-0.6) {\textbf{After: Single Enclave}};
\draw[fill=green!20,thick] (0,-1.8) rectangle (7,-0.8);
\node at (3.5,-2.05) {Single Consolidated Enclave};

% Tasks inside consolidated enclave
\foreach \i in {0.5,3,5.5} {
  \draw[fill=blue!10,thick] (\i,-1.6) rectangle +(1,0.6);
  \node at (\i+0.5,-1.3) {Task};
}

% Optional legend
\begin{scope}[shift={(8,0)}]
  \draw[fill=red!20] (0,1.5) rectangle +(0.5,0.3);
  \node[right] at (0.6,1.65) {Separate Enclave};
  \draw[fill=green!20] (0,1) rectangle +(0.5,0.3);
  \node[right] at (0.6,1.15) {Consolidated Enclave};
  \draw[fill=blue!10] (0,0.5) rectangle +(0.5,0.3);
  \node[right] at (0.6,0.65) {Task};
\end{scope}

    }
    \only<3>{\item \faRetweet\ \textbf{Reduce switching costs:} Batch enclave calls to limit context switches and improve throughput.
    \begin{figure}[H]
\centering
\begin{tikzpicture}[>=stealth,thick,font=\scriptsize,scale=0.9]
  % === Left: Unbatched ===
  \fill[green!10] (0,0) rectangle (2.5,2.5);
  \fill[blue!10] (2.5,0) rectangle (5,2.5);

  \node at (1.25,2.7) {\textbf{Enclave}};
  \node at (3.75,2.7) {\textbf{Host}};

  \draw[dashed,thick] (2.5,0) -- (2.5,2.5) node[midway,above,sloped];

  \draw[->,red!70!black] (0.8,2.0) -- (3.2,2.0) node[midway,above]{Call 1};
  \draw[->,red!70!black] (0.8,1.4) -- (3.2,1.4) node[midway,above]{Call 2};
  \draw[->,red!70!black] (0.8,0.8) -- (3.2,0.8) node[midway,above]{Call 3};

  \node[align=center] at (2.5,-0.6) {\textbf{Unbatched}\\Multiple crossings};

  % === Right: Batched ===
  \begin{scope}[shift={(6,0)}]
    \fill[green!10] (0,0) rectangle (2.5,2.5);
    \fill[blue!10] (2.5,0) rectangle (5,2.5);

    \node at (1.25,2.7) {\textbf{Enclave}};
    \node at (3.75,2.7) {\textbf{Host}};

    \draw[dashed,thick] (2.5,0) -- (2.5,2.5) node[midway,above,sloped];

\draw[->,red!70!black,thick] (0.8,1.3) -- (2.8,1.3) 
    node[midway,above]{Batched Call}
    node[midway,below=4pt,draw,fill=orange!20,rounded corners=2pt,
         inner xsep=4pt,inner ysep=2pt]{Batch Processor};

    \node[align=center] at (2.5,-0.6) {\textbf{Batched}\\One crossing};
  \end{scope}

\end{tikzpicture}
\caption{Unbatched vs Batched enclave-to-host calls}
\end{figure}

    }
    \only<4>{\item \faCode\ \textbf{Offload heavy lifting:} Run non-sensitive, high-load tasks outside enclaves for efficiency. \\
\begin{tikzpicture}[
    font=\scriptsize,
    >=Stealth,
    thick,
    task/.style={
        fill=blue!10,
        rounded corners=1pt,
        minimum width=2.6cm,
        minimum height=0.45cm,
        draw
    },
    box/.style={
        rounded corners=2pt,
        minimum height=2.4cm,
        draw,
        thick
    }
]

% --- Enclave ---
\node[box,fill=green!20,minimum width=3.5cm,anchor=north west,
      label={[font=\bfseries]above:Enclave}] (enclave) at (0,0) {};
\node at ([yshift=-0.3cm]enclave.north) {Sensitive Tasks Only};

% Sensitive tasks inside enclave
\node[task] at ([yshift=-0.9cm]enclave.north) {Crypto Ops};
\node[task] at ([yshift=-1.5cm]enclave.north) {ML Inference};
\node[task] at ([yshift=-2.1cm]enclave.north) {Attestation};

% --- Host area ---
\node[box,fill=gray!15,minimum width=3.5cm,anchor=north west,
      label={[font=\bfseries]above:Host}] (host) at (5,0) {};
\node at ([yshift=-0.3cm]host.north) {Non‑Sensitive Tasks};

% Non-sensitive tasks outside
\node[task] at ([yshift=-0.9cm]host.north) {Bulk Encryption};
\node[task] at ([yshift=-1.5cm]host.north) {Data Prep};

% --- Arrow & label ---
\draw[->,ultra thick]
    ([yshift=-0.9cm]enclave.east) -- ([yshift=-0.9cm]host.west)
    node[midway,above,font=\scriptsize] {Offload};

% --- Legend ---
\begin{scope}[shift={(0,-3)}]
  \draw[fill=green!20,rounded corners=1pt] (0,0) rectangle +(0.35,0.2);
  \node[right] at (0.45,0.1) {Enclave};
  \draw[fill=gray!15,rounded corners=1pt] (2,0) rectangle +(0.35,0.2);
  \node[right] at (2.45,0.1) {Host};
  \draw[fill=blue!10,rounded corners=1pt] (4,0) rectangle +(0.35,0.2);
  \node[right] at (4.45,0.1) {Task};
\end{scope}

\end{tikzpicture}
    }
\end{itemize}
\end{block}

\only<5>{
\begin{alertblock}{Key Principle}
    \textbf{Optimize the trade-off:} Balance performance, isolation, and PMP resource usage for maximum efficiency.
\end{alertblock}
}
\end{frame}

@@

\section{Future Directions and Conclusion}
% Future Work and Improvements
\begin{frame}{Hardware Outlook \& Future Directions}
    \only<1>{
\begin{block}{Limitations}
\begin{itemize}
    \item Few PMP entries.
    \item Rigid NAPOT region encoding.
\end{itemize}
\end{block}
    }
    \only<2>{
\begin{alertblock}{Future Opportunities}
\begin{itemize}
    \item More flexible PMP schemes.
    \item Crypto accelerators for enclave workloads.
    \item Software-defined memory isolation models.
\end{itemize}
\end{alertblock}
    }
\end{frame}
